infer: An R package for tidyverse-friendly statistical inference

### 2021-07-30 figs/paper/paper.Rmd
note `mosaic`, adjust citation

`broom` and `parameters` convert model objects to unified output formats, though they do not provide methods for fitting models, describing null distributions, performing bootstrapping, or calculating summary statistics from tabular data. `statsexpressions`, and adjacent packages in the `easystats` ecosystem, implement wrappers with consistent interfaces for theory-based hypothesis tests. At a higher level, the structure of each of these packages is defined by model types, where each model type has its own associated function and/or model object. In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar. `infer`'s initial release on the Comprehensive R Archive Network predated that of each of the packages mentioned above, with the exception of `broom`, a package situated in the same `tidymodels` ecosystem [@CRAN].

>>>>

Several software packages on the Comprehensive R Archive Network share functionality with `infer` [@CRAN]. `broom` and `parameters` convert model objects to unified output formats, though they do not provide methods for fitting models, describing null distributions, performing bootstrapping, or calculating summary statistics from tabular data. `statsexpressions`, and adjacent packages in the `easystats` ecosystem, implement wrappers with consistent interfaces for theory-based hypothesis tests. Similarly, `mosaic` is a package used to teach statistics by unifying summary statistics, visualization, and modeling with a consistent API built around R's formula interface. The `mosaic` package also includes functionality to conduct randomization-based inference. At a higher level, though, the structure of each of these packages is defined by model types and statistics, where each model type or statistic has its own associated function and/or object class. In contrast, `infer` is structured around four functions, situating statistics and model types within a more abstracted grammar.^[This grammar follows from Allen Downey's "there is only one test" framework [@downey2016].]

### 2021-07-30 figs/paper/paper.tex
note `mosaic`, adjust citation

\texttt{broom} and \texttt{parameters} convert model objects to unified
output formats, though they do not provide methods for fitting models,
describing null distributions, performing bootstrapping, or calculating
summary statistics from tabular data. \texttt{statsexpressions}, and
adjacent packages in the \texttt{easystats} ecosystem, implement
wrappers with consistent interfaces for theory-based hypothesis tests.
At a higher level, the structure of each of these packages is defined by
model types, where each model type has its own associated function
and/or model object. In contrast, \texttt{infer} is structured around
four functions, situating statistics and model types within a more
abstracted grammar.\footnote{This grammar follows from Allen Downey's
  ``there is only one test'' framework (Downey, 2011).} \texttt{infer}'s
initial release on the Comprehensive R Archive Network predated that of
each of the packages mentioned above, with the exception of
\texttt{broom}, a package situated in the same \texttt{tidymodels}
ecosystem (R Core Team, 2021).

@@

\leavevmode\hypertarget{ref-downey2011think}{}%
Downey, A. B. (2011). \emph{Think stats}. " O'Reilly Media, Inc.".

>>>>

Several software packages on the Comprehensive R Archive Network share
functionality with \texttt{infer} (R Core Team, 2021). \texttt{broom}
and \texttt{parameters} convert model objects to unified output formats,
though they do not provide methods for fitting models, describing null
distributions, performing bootstrapping, or calculating summary
statistics from tabular data. \texttt{statsexpressions}, and adjacent
packages in the \texttt{easystats} ecosystem, implement wrappers with
consistent interfaces for theory-based hypothesis tests. Similarly,
\texttt{mosaic} is a package used to teach statistics by unifying
summary statistics, visualization, and modeling with a consistent API
built around R's formula interface. The \texttt{mosaic} package also
includes functionality to conduct randomization-based inference. At a
higher level, though, the structure of each of these packages is defined
by model types and statistics, where each model type or statistic has
its own associated function and/or object class. In contrast,
\texttt{infer} is structured around four functions, situating statistics
and model types within a more abstracted grammar.\footnote{This grammar
  follows from Allen Downey's ``there is only one test'' framework
  (Downey, 2016).}

@@

\leavevmode\hypertarget{ref-downey2016}{}%
Downey, A. B. (2016). There is still only one test.
